Dissertation draft

### 2023-07-25 Texfiles/Draft1.tex
More words finally

In retiree's first year of retirement I allow them to choose to annuitise some of their wealth. In practical terms
this is moving down the asset grid but up the income grid and seeing if the value of being in that position is better
than where the individual is currently. To assess this trade-off I calculate the annual annuity payment that follows
from a given annuity cost. I calculate this using objective life tables from the ONS using the following equation:

@@

I also simulate the expected change in consumption given different rates of annuitisation versus no annuitisation.
The benefit of simulating an individual's decision is that we can directly compare what they would have
consumed with what they actually consumed, and we can replicate the empirical analysis using the
solution to the lifecycle model.

@@

    \input{tables/standard_life_cycle.tex}
\end{landscape}

Table \ref{tab:StandardLifeCycle} shows the results from the bequest models.

>>>>

\textbf{I don't actually know why I do this}
In retiree's first year of retirement I allow them to choose to annuitise some of their wealth. In practical terms
this is moving down the asset grid but up the income grid and seeing if the value of being in that position is better
than where the individual is currently. To assess this trade-off I calculate the annual annuity payment that follows
from a given annuity cost. I calculate this using objective life tables from the ONS using the following equation:

@@

\section{Lifecycle Results}

Having found optimal policy functions and value functions I can now simulate the change in consumption given
different rates of annuitisation versus no annuitisation.
There are multiple benefits to building a model of individuals decisions. Firstly, we can directly compare
what a given individual would have consumed with what they actually consumed, conditional on our model being
correct. In other words we have the counterfactual world in which individuals were not forced to annuitise.
Secondly, we can simulate the impact of different policy changes on the consumption, savings and bequest behaviour.
For example, I can change the proportion of wealth that will be annuitised and see the corresponding changes in
consumption indicators for all individuals.

I start this section by plotting the retirement path of consumption for a median individual in
the ELSA data set. I plot consumption with different proportions of starting wealth annuitised
and the different lifecycle model types.

\begin{figure}[h]
    \caption{Consumption in retirement}
    \centering
    \includegraphics[width=0.7\columnwidth]{figures/consumption_plot_median_retiree.pdf}
    \label{fig:ConsumpPlot}
\end{figure}

\begin{figure}[h]
    \caption{Assets in retirement}
    \centering
    \includegraphics[width=0.7\columnwidth]{figures/asset_plot_median_retiree.pdf}
    \label{fig:AssetPlot}
\end{figure}

Figures \ref{fig:ConsumpPlot} and \ref{fig:AssetPlot} show the retirement
path of consumption and assets for a median retiree. This hypothetical women has
120,000 of assets at age 65 when they retired in 2012 with a state pension income of 6000.
The dashed lines show consumption and assets with an annuity that costs half of their wealth.
This buys them 3500 of annuity income, which, given their objective life expectancies is a money's
worth of about 90\%.

We can see that the asset path with the bequest motive keeps more for longer but still decreases
and by their late 90s they have completely run down their wealth. Interestingly the asset path
with the quickest run down is the standard lifecycle model using objective life expectancies,
which points towards this individual being infact optimistic about their life chances.
Also rather surprisingly the asset paths of all three types are similar without annuities.
The paths only diverge after age 75 at which point the bequest path stays high and the
other paths start to decrease faster. This is contrary to the path with annuities where
the standard path diverges from the bequest and subjective paths immediately.

The consumption paths all start at around 1400. The three models without an annuity start at
exactly the same amount and stay that way until the individual reaches her mid seventies -- showing
that even quite different lifecycle models can generate similar paths. As expected, the consumption
path with the bequest motive with an annuity is lower at the start of retirement than the bequest path 
without an annuity as individuals seek to build their savings back up.
But it is also lower for the subjective life expectancy case,
again pointing toward this individual being optimistic. However, the subjective consumption
line rises at a younger age than the line with bequests, showing that the models align 
with the prediction that subjective lifecycle agents consume more in early retirement.

The period of interest in this study is the first three years of retirement. For this period 
we do see substantially differences in consumption for the diffe

@@

\begin{landscape}
    \input{tables/standard_life_cycle.tex}
\end{landscape}

Table \ref{tab:StandardLifeCycle} shows the results from the standard model lifecycle when individuals use ONS
for risk of death and have no bequest function. In this case .
